Supplementary Information

### 2020-11-15 doc/manuscript/MEE_manuscript_SI.Rmd
copy over formal comparison figs

# MOVE FIGURE FILES
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/composite_plots/")

>>>>

# MOVE FIGURE FILES
#traditional comparison
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/formal_comparison/figures/", "^climwin_vs_dcc_.+[.]png$", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/traditional_comparison/")

#composite plots
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/composite_plots/")
